\begin{招待講演}{1}
%Kuga先生
\bibitem{ykuga458xxxxx}
空閑洋平, mdx: アカデミックHPCクラウドmdxの紹介と今後の技術課題, PCクラスタワークショップ, 2024年6月.

%華井先生
\bibitem{hanai-kyudai}
華井雅俊、 
"ARIM-mdxデータシステム:材料研究向け実験・シミュレーションの統合データプラットフォーム"、
ARIM次世代ナノスケールマテリアル領域 研究会、
2025年3月

\bibitem{hanai-akiba}
華井雅俊、 
"ARIM-mdxデータシステム:材料研究向け実験・シミュレーションの統合データプラットフォーム"、
第19回材料系ワークショップ、
2025年2月

\bibitem{hanai-simpo}
華井雅俊、
"東京大学ARIM データ基盤部門 活動報告",
ARIM「第3回革新的なエネルギー変換を可能とするマテリアル領域」シンポジウム,
2024年12月

\bibitem{hanai-mdx}
華井雅俊、
"ARIM-mdxデータシステム:材料研究向け実験・シミュレーションの統合データプラットフォーム"、
データ活用社会創成シンポジウム2024、
2024年12月

\bibitem{hanai-nbci}
華井雅俊、 
"ARIM-mdx データ収集・保存システムの紹介"、
第2回 NBCI-ARIM 技術交流会、
2024年6月

\end{招待講演}

%\begin{招待論文}{1}

%\end{招待論文}


%\begin{受賞}{1}

%\end{受賞}

% \begin{著書}{1}

% \end{著書}

\begin{雑誌論文}{1}
%小林先生
\bibitem{kobayashi1-1}
Zekun Cai, Renhe Jiang, Xinlei Lian, Chuang Yang, Zhaonan Wang, Zipei Fan, Kota Tsubouchi, Hill Hiroki Kobayashi, Xuan Song, Ryosuke Shibasaki,  "Forecasting Citywide Crowd Transition Process via Convolutional Recurrent Neural Networks", IEEE Transactions on Mobile Computing 23(5) 5433 - 5445.

%河村先生
\bibitem{kawamura_hphi}
K. Ido, M. Kawamura, Y. Motoyama, K. Yoshimi, Y. Yamaji, S. Todo, N. Kawashima, T. Misawa, 
``Update of $\mathcal{H}\Phi$: Newly added functions and methods in versions 2 and 3'',
Comp. Phys. Commun. \textbf{298}, 109093 (2024).

\bibitem{kawamura_pdcu111}
W. Osada, M. Hasegawa, Y. Shiozawa, K. Mukai, S. Yoshimoto, S. Tanaka, M. Kawamura, T. Ozaki and J. Yoshinobu, 
``Chemical process of hydrogen and formic acid on a Pd-deposited Cu(111) surface studied by high-resolution X-ray photoelectron spectroscopy and density functional theory calculations'',
Phys. Chem. Chem. Phys. \textbf{27}, 1978 (2025).

\bibitem{kawamura_wo2}
Y. Muramatsu, D. Hirai, M. Kawamura, S. Minami, Y. Ikeda, T. Shimada, K. Kojima, N. Katayama, K. Takenaka, 
``Topological electronic structure and transport properties of the distorted rutile-type WO$_2$''
APL Mater. \textbf{13}, 011119 (2025).

\bibitem{kawamura_omax}
M. Keivanloo, M. Sandoghchi, M. Reza Mohammadizadeh, M. Kawamura, H. Raebiger, K. Hongo, R. Maezono and M. Khazaei, 
``Superconductivity in o-MAX phases''
Nanoscale, \textbf{17}, 5341 (2025).

\bibitem{kawamura_kmgh3}
S. Lu, R. Akashi, M. Kawamura, S. Tsuneyuki, 
``Assessing the possible superconductivity in doped perovskite hydride KMgH$_3$: Effects of lattice anharmonicity and spin fluctuations''
Phys. Rev. B \textbf{111}, 134516 (2025).

%Li先生
\bibitem{ireneli-1}
Rui Yang, Qingcheng Zeng, Keen You, Yujie Qiao, Lucas Huang, Chia-Chun Hsieh, Benjamin Rosand, Jeremy Goldwasser, Amisha D. Dave, Tiarnan D. L. Keenan, Yuhe Ke, Cheng Hong, Nan Liu, Emily Y. Chew, Dragomir Radev, Zhiyong Lu, Hua Xu, Qingyu Chen, and Irene Li,\lq\lq Ascle—A Python Natural Language Processing Toolkit for Medical Text Generation: Development and Evaluation Study," Journal of Medical Internet Research, vol. 26, 2024.


\bibitem{ireneli-2}
Yuhe Ke, Rui Yang, Sui An Lie, Taylor Xin Yi Lim, Yilin Ning, Irene Li, Hairil Rizal Abdullah, Daniel Shu Wei Ting, and Nan Liu, \lq\lq Mitigating Cognitive Biases in Clinical Decision-Making Through Multi-Agent Conversations Using Large Language Models: Simulation Study,” Journal of Medical Internet Research, vol. 26, 2024.

\bibitem{ireneli-3}
Han Yuan, Mingcheng Zhu, Rui Yang, Han Liu, Irene Li, Chuan Hong, \lq\lq Rethinking Domain-Specific Pretraining by Supervised or Self-Supervised Learning for Chest Radiograph Classification: A Comparative Study Against ImageNet Counterparts in Cold-Start Active Learning," Health Care Science, vol. 3, no. 2, 2025.

\bibitem{ireneli-4}
Dairui Liu, Derek Greene, Irene Li, Xuefei Jiang, and Ruihai Dong, \lq\lq Topic-Centric Explanations for News Recommendation," ACM Transactions on Recommender Systems, vol. 3, no. 2, 2024, Article 9.

\end{雑誌論文}

\begin{査読付}{1}
%小林先生
\bibitem{kobayashi2-1}
Zhuoneng Sui, Haoran Hong, Daisuké Shimotoku, Hill Hiroki Kobayashi, "catAction: Deep learning for enhancing emotional cat-human interactions through the posture-based determination of the degrees of kittens' defensive and offensive aggressions.", Proceedings of the International Conference on Animal-Computer Interaction(ACI) 5-9, 202.  

%鈴村先生
\bibitem{ega}
Toyotaro Suzumura, Hiroki Kanezashi, Shotaro Akahori, "Graph Adapter for Parameter-Efficient Fine-Tuning of EEG Foundation Models", The 39th Annual AAAI Conference on Artificial Intelligence (AAAI-25), The 9th International Workshop on Health Intelligence (W3PHIAI-25), 2025.

\bibitem{gefm}
Limin Wang, Toyotaro Suzumura, Hiroki Kanezashi, "GEFM: Graph-Enhanced EEG Foundation Model", The 39th Annual AAAI Conference on Artificial Intelligence (AAAI-25), Workshop on Large Language Models and Generative AI for Health (GenAI4Health), 2025.

\bibitem{awrs}
 Igor L.R. Azevedo, Toyotaro Suzumura, Yuichiro Yasui, "A Look Into News Avoidance Through AWRS : An Avoidance-Aware Recommender System", Proceedings of the 2025 SIAM International Conference on Data Mining (SDM). Society for Industrial and Applied Mathematics, 2025.

\bibitem{annealing-gnn}
Pablo Loyola, Kento Hasegawa, Andrés Hoyos-Idrobo, Kazuo Ono, Toyotaro Suzumura, Yu Hirate, Masanao Yamaoka, "Annealing Machine-assisted Learning of Graph Neural Network for Combinatorial Optimization", In NeurIPS 2024 Workshop Machine Learning with new Compute Paradigms, 2024.

\bibitem{aln}
Md Mostafizur Rahman, Daisuke Kikuta, Yu Hirate, and Toyotaro Suzumura, "Graph-Based Audience Expansion Model for Marketing Campaigns" In Proceedings of the 47th International ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR '24). Association for Computing Machinery, New York, NY, USA, 2970–2975, 2024.

\bibitem{p4r}
Chen, Junyi, Toyotaro Suzumura. "A Prompting-Based Representation Learning Method for Recommendation with Large Language Models." The 1st Workshop on Risks, Opportunities, and Evaluation of Generative Models in Recommender Systems (ROEGEN@RECSYS'24), 2024.

%華井先生
\bibitem{hanai-BigData}
Masatoshi Hanai, Mitsuaki Kawamura, Ryo Ishikawa, Toyotaro Suzumura, Kenjiro Taura
"ARIM-mdx Data System: Towards a Nationwide Data Platform for Materials Science"
In Proceedings of the 2024 IEEE International Conference on Big Data (BigData), December, 2024, US.

%河村先生
\bibitem{kawamura_hanai_tone_continuousp}
Y. Tone, M. Hanai, M. Kawamura, K. Taura, T. Suzumura,
``ContinuouSP: Generative Model for Crystal Structure Prediction with Invariance and Continuity'',
 4th Annual AAAI Workshop on AI to Accelerate Science and Engineering (AI2ASE), 2024.
 
%LI先生
\bibitem{ireneli-5}
Dairui Liu, Boming Yang, Honghui Du, Derek Greene, Neil Hurley, Aonghus Lawlor, Ruihai Dong, and Irene Li, \lq \lq RecPrompt: A Self-Tuning Prompting Framework for News Recommendation Using Large Language Models," Proceedings of the 33rd ACM International Conference on Information and Knowledge Management (CIKM), 2024.

\bibitem{ireneli-6}
Yingjian Chen, Haoran Liu, Yinhong Liu, Jinxiang Xie, Rui Yang, Han Yuan, Yanran Fu, Pengyuan Zhou, Qingyu Chen, James Caverlee, and Irene Li, \lq\lq GraphCheck: Breaking Long-Term Text Barriers with Extracted Knowledge Graph-Powered Fact-Checking," Proceedings of the 63rd Annual Meeting of the Association for Computational Linguistics (ACL), 2025.

\end{査読付}

\begin{公開}{1}
%華井先生
\bibitem{hanai-arim-mdx}
"ARIM-mdxデータシステム",
\url{https://arim.mdx.jp/},


\end{公開}

%\begin{特許}{1}

%\end{特許}

\begin{発表}{1}

%宮本先生
\bibitem{dmiya1}
手塚 尚哉, 宮本 大輔, 明石 邦夫, 落合 秀也, ファイルの侵害をフックすることによる ランサムウェアからのデータ保護システム, コンピュータセキュリティシンポジウム, 2024年10月

%川瀬先生
\bibitem{kawase01}
川瀬純也: 配列アライメントを用いた放牧牛の移動行動クラスタリング手法の検討, 動物の行動と管理学会 2024年度研究発表会, 熊本, 2024.9

\bibitem{kawase02}
川瀬純也: 配列アライメントを用いた放牧牛の移動行動クラスタリングの試み, 第33回地理情報システム学会学術研究発表大会, P2-19, 京都, 2024.10

%華井先生
\bibitem{hanai-press}
「材料研究DXを加速するARIM-mdxデータシステムを開発、全国の900名以上が利用開始」,
\url{https://www.u-tokyo.ac.jp/focus/ja/press/z0310_00004.html},

\bibitem{hanai-rxt}
「ハウディ、東京大学との共同研究から生まれたデータ転送IoTデバイス「RxT-01」を販売開始」,
\url{https://prtimes.jp/main/html/rd/p/000000012.000083225.html},

%Kuga先生
\bibitem{ykuga4301yyyyy}
LLM-jp, LLM-jp: A Cross-organizational Project for the Research and Development of Fully Open Japanese LLMs, arXiv preprint, 2024.

\bibitem{ykuga4301xyyyy}
空閑洋平, 中村遼, ソフトウェアメモリを用いたデバイス間データ通信の機能拡張手法の検討, コンピュータシステム・シンポジウム (Comsys), 2024年12月.

%Li先生
\bibitem{ireneli-7}
Rui Yang, Boming Yang, Aosong Feng, Sixun Ouyang, Moritz Blum, Tianwei She, Yuang Jiang, Freddy Lecue, Jinghui Lu, and Irene Li, \lq\lq Graphusion: A RAG Framework for Knowledge Graph Construction with a Global Perspective,"
International Workshop on Natural Language Processing for Knowledge Graph Construction, WWW, 2025. 

\bibitem{ireneli-8}
Yingjian Chen, Feiyang Li, Xingyu Song, Tianxiao Li, Zixin Xu, Xiujie Chen, Issey Sukeda, and Irene Li,
\lq\lq Exploring the Role of Knowledge Graph-Based RAG in Japanese Medical Question Answering with Small-Scale LLMs," Workshop on Improving Healthcare with Small Language Models, AIME 2025. 

\end{発表}

% \begin{特記}{1}

% \end{特記}

%\begin{報道}{1}

%end{報道}
