\begin{雑誌論文}{4}
\bibitem{kawamura_hphi}
K. Ido, M. Kawamura, Y. Motoyama, K. Yoshimi, Y. Yamaji, S. Todo, N. Kawashima, T. Misawa, 
``Update of $\mathcal{H}\Phi$: Newly added functions and methods in versions 2 and 3'',
Comp. Phys. Commun. \textbf{298}, 109093 (2024).

\bibitem{kawamura_pdcu111}
W. Osada, M. Hasegawa, Y. Shiozawa, K. Mukai, S. Yoshimoto, S. Tanaka, M. Kawamura, T. Ozaki and J. Yoshinobu, 
``Chemical process of hydrogen and formic acid on a Pd-deposited Cu(111) surface studied by high-resolution X-ray photoelectron spectroscopy and density functional theory calculations'',
Phys. Chem. Chem. Phys. \textbf{27}, 1978 (2025).

\bibitem{kawamura_wo2}
Y. Muramatsu, D. Hirai, M. Kawamura, S. Minami, Y. Ikeda, T. Shimada, K. Kojima, N. Katayama, K. Takenaka, 
``Topological electronic structure and transport properties of the distorted rutile-type WO$_2$''
APL Mater. \textbf{13}, 011119 (2025).

\bibitem{kawamura_omax}
M. Keivanloo, M. Sandoghchi, M. Reza Mohammadizadeh, M. Kawamura, H. Raebiger, K. Hongo, R. Maezono and M. Khazaei, 
``Superconductivity in o-MAX phases''
Nanoscale, \textbf{17}, 5341 (2025).

\bibitem{kawamura_kmgh3}
S. Lu, R. Akashi, M. Kawamura, S. Tsuneyuki, 
``Assessing the possible superconductivity in doped perovskite hydride KMgH$_3$: Effects of lattice anharmonicity and spin fluctuations''
Phys. Rev. B \textbf{111}, 134516 (2025).
\end{雑誌論文}

\begin{査読付}{3}
\bibitem{kawamura_hanai_tone_continuousp}
Y. Tone, M. Hanai, M. Kawamura, K. Taura, T. Suzumura,
``ContinuouSP: Generative Model for Crystal Structure Prediction with Invariance and Continuity'',
 4th Annual AAAI Workshop on AI to Accelerate Science and Engineering (AI2ASE), 2024.
\end{査読付}
