% \begin{雑誌論文}{1}

% \bibitem{sample}
% Irene Li, Jessica Pan, Jeremy Goldwasser, Neha Verma, Wai Pan Wong, Muhammed Yavuz Nuzumlalı, Benjamin Rosand, Yixin Li, Matthew Zhang, David Chang, R. Andrew Taylor, Harlan M. Krumholz, Dragomir Radev,\lq\lq Neural Natural Language Processing for unstructured data in electronic health records: A review", Computer Science Review, volume 46, 2022.

% \end{雑誌論文}

% \begin{査読付}{1}

% \bibitem{feng2022diffuser}
% Aosong Feng and Irene Li and Yuang Jiang andRex  Ying,\lq\lq Diffuser: Efficient Transformers with Multi-hop Attention Diffusion for Long Sequences", Proceedings of Thirty-Seventh AAAI Conference on Artificial Intelligence (AAAI), 2023.

% \end{査読付}

% \begin{発表}{1}

% \bibitem{li2023nnkgc}
% Zihui Li and Boming Yang and Toyotaro Suzumura,\lq\lq NNKGC: Improving Knowledge Graph Completion with Node Neighborhoods", arXiv preprint, 2023.

% \end{発表}

% \begin{招待講演}{1}  % invited talks

% sample
% \bibitem{sample-kobayashi3-1}
% Hill Hiroki Kobayashi, mdx: A Cloud Platform for Supporting Data Science and Cross-Disciplinary Research Collaborations, the Nepal JSPS Alumni Association (NJAA), hosted its 7th Symposium, 29 November, 2022.

% \bibitem{ireneli-1}
% Irene Li, A Journey from Transformers to Large Language Models: an Educational Perspective, 2023 the 1st International Conference on AI-generated Content (AIGC2023), Aug, 2023


% \end{招待講演}  % end: invited talks

% \begin{招待論文}{1}  % invited papers



% \end{招待論文}  % end: invited papers


% \begin{受賞}{1}  % awards

% \bibitem{ireneli-2}
% Boming Yang, Dairui Liu, Toyotaro Suzumura, Ruihai Dong and Irene Li,\lq\lq Going Beyond Local: Global Graph-Enhanced Personalized News Recommendations", Proceedings of the 17th ACM Conference on Recommender Systems  (RecSys 2023), 2023 (Best Student Paper Award)

% \end{受賞}  % end: awards


% \begin{著書}{1}  % books

% \end{著書}  % end: books


\begin{雑誌論文}{1}  % journals

% % sample
% % \bibitem{sample-kobayashi1-3}
% % Wenjing Li, Haoran Zhang, Jinyu Chen, Peiran Li, Yuhao Yao, Xiaodan Shi,  Mariko Shibasaki, Hill Hiroki Kobayashi, Xuan Song and Ryosuke Shibasaki, \lq\lq Metagraph-Based Life Pattern Clustering With Big Human Mobility Data", IEEE Transactions on Big Data, Feb, 2023.

\bibitem{ireneli-1}
Rui Yang, Qingcheng Zeng, Keen You, Yujie Qiao, Lucas Huang, Chia-Chun Hsieh, Benjamin Rosand, Jeremy Goldwasser, Amisha D. Dave, Tiarnan D. L. Keenan, Yuhe Ke, Cheng Hong, Nan Liu, Emily Y. Chew, Dragomir Radev, Zhiyong Lu, Hua Xu, Qingyu Chen, and Irene Li,\lq\lq Ascle—A Python Natural Language Processing Toolkit for Medical Text Generation: Development and Evaluation Study," Journal of Medical Internet Research, vol. 26, 2024.


\bibitem{ireneli-2}
Yuhe Ke, Rui Yang, Sui An Lie, Taylor Xin Yi Lim, Yilin Ning, Irene Li, Hairil Rizal Abdullah, Daniel Shu Wei Ting, and Nan Liu, \lq\lq Mitigating Cognitive Biases in Clinical Decision-Making Through Multi-Agent Conversations Using Large Language Models: Simulation Study,” Journal of Medical Internet Research, vol. 26, 2024.

\bibitem{ireneli-3}
Han Yuan, Mingcheng Zhu, Rui Yang, Han Liu, Irene Li, Chuan Hong, \lq\lq Rethinking Domain-Specific Pretraining by Supervised or Self-Supervised Learning for Chest Radiograph Classification: A Comparative Study Against ImageNet Counterparts in Cold-Start Active Learning," Health Care Science, vol. 3, no. 2, 2025.

\bibitem{ireneli-4}
Dairui Liu, Derek Greene, Irene Li, Xuefei Jiang, and Ruihai Dong, \lq\lq Topic-Centric Explanations for News Recommendation," ACM Transactions on Recommender Systems, vol. 3, no. 2, 2024, Article 9.

\end{雑誌論文}  % end: journals


\begin{査読付}{1}  % papers (peer-reviewed)

\bibitem{ireneli-5}
Dairui Liu, Boming Yang, Honghui Du, Derek Greene, Neil Hurley, Aonghus Lawlor, Ruihai Dong, and Irene Li, \lq \lq RecPrompt: A Self-Tuning Prompting Framework for News Recommendation Using Large Language Models," Proceedings of the 33rd ACM International Conference on Information and Knowledge Management (CIKM), 2024.

\bibitem{ireneli-6}
Yingjian Chen, Haoran Liu, Yinhong Liu, Jinxiang Xie, Rui Yang, Han Yuan, Yanran Fu, Pengyuan Zhou, Qingyu Chen, James Caverlee, and Irene Li, \lq\lq GraphCheck: Breaking Long-Term Text Barriers with Extracted Knowledge Graph-Powered Fact-Checking," Proceedings of the 63rd Annual Meeting of the Association for Computational Linguistics (ACL), 2025.

% sample
% \bibitem{sample-kobayashi2-1}
% Daisuk\'e Shimotoku, Tian Yuan, Laxmi Kumar Parajuli and Hill Hiroki Kobayashi,\lq\lq Participatory Sensing Platform Concept for Wildlife Animals in the Himalaya Region, Nepal", Proceedings of 2022 International Conference on Human-Computer Interaction (HCII 2022), 2022.  

\end{査読付}  % end: papers (peer-reviewed)


% \begin{公開}{1}  % open-source urls


% \end{公開}  % end: open-source urls


% \begin{特許}{1}  % patents

% \end{特許}  % end: patents


\begin{発表}{1}  % other talks (Not peer reviewed)

\bibitem{ireneli-7}
Rui Yang, Boming Yang, Aosong Feng, Sixun Ouyang, Moritz Blum, Tianwei She, Yuang Jiang, Freddy Lecue, Jinghui Lu, and Irene Li, \lq\lq Graphusion: A RAG Framework for Knowledge Graph Construction with a Global Perspective,"
International Workshop on Natural Language Processing for Knowledge Graph Construction, WWW, 2025. 

\bibitem{ireneli-8}
Yingjian Chen, Feiyang Li, Xingyu Song, Tianxiao Li, Zixin Xu, Xiujie Chen, Issey Sukeda, and Irene Li,
\lq\lq Exploring the Role of Knowledge Graph-Based RAG in Japanese Medical Question Answering with Small-Scale LLMs," Workshop on Improving Healthcare with Small Language Models, AIME 2025. 


\end{発表}  % end: other talks (Not peer reviewed)


% \begin{報道}{1}  % press (news paper,  televison, etc.)

% \bibitem{ireneli-13}
% (Interview) Gemma Conroy, \textit{How ChatGPT and other AI tools could disrupt scientific publishing} \footnote{https://www.nature.com/articles/d41586-023-03144-w}, \textbf{Nature, Featured News}, 10 October 2023 

% \end{報道}  % end: press (news paper, televison, etc.)

